On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-07-17 Manuscript/manuscript.tex
Fixed 1 thing

Figure~\ref{fig:Scatterplot2019vs2022} shows the distribution of times from the
2019 and 2022 World Championships.  
\eds{Please reorganize the labels so they are either in one of the following 
orders:
2019 Heat, 2019 Semi, 2019 final, 2022 Heat, 2022 Semi, 2022 final  OR
2019 Heat, 2022 Heat, 2019 Semi, 2022 Semi, 2019 final, 2022 final.  
(I am not sure which is better, but perhaps the latter?)}
This data was only for athletes who competed
in at least one race at each championship, however it is possible for athletes
to have competed in one race in 2019 and two races in 2022.  The 2022 World
Championship Heats and Semifinals both had on average lower reaction times than
their respective 2019 races, and the 2022 finals were substantially faster. Also
worth noting is that the fastest reaction time in the 2022 Finals and 2022
Semifinals both came from Devon Allen, but the difference between 0.101 and 0.009
seconds was the difference in what caused him to be disqualified. \eds{check 
these numbers? 0.099?}

>>>>

Figure~\ref{fig:Scatterplot2019vs2022} shows the distribution of times from the
2019 and 2022 World Championships.  
\eds{Please reorganize the labels so they are either in one of the following 
orders:
2019 Heat, 2019 Semi, 2019 final, 2022 Heat, 2022 Semi, 2022 final  OR
2019 Heat, 2022 Heat, 2019 Semi, 2022 Semi, 2019 final, 2022 final.  
(I am not sure which is better, but perhaps the latter?)}
This data was only for athletes who competed
in at least one race at each championship, however it is possible for athletes
to have competed in one race in 2019 and two races in 2022.  The 2022 World
Championship Heats and Semifinals both had on average lower reaction times than
their respective 2019 races, and the 2022 finals were substantially faster. Also
worth noting is that the fastest reaction time in the 2022 Finals and 2022
Semifinals both came from Devon Allen, but the difference between 0.101 and 0.099
seconds was the difference in what caused him to be disqualified. \eds{check 
these numbers? 0.099?}\of{resolved}
